---
title: "Lab Data Analysis"
author: "Braeden Grenier"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat = read.csv("plottingnoacetone.csv")
dat
```

#Loading the libraries necessary to run the code
```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
```


#GRAPHING

##Some Calculations
```{r}
dat = dat %>% mutate(dat,
  Concentration_in_plate = AbsorbanceCorrected / (30000 * 0.5),
  Mol_in_plate = Concentration_in_plate * 0.2,
  Anthocyanin_in_root = Mol_in_plate/Sample.Weight
)
dat
```
The above code generates 3 important values for our data, Concentration of anthocyanin in the microplate, the absolute amount of mols in the microplate, and the anthocyanin per gram of root tissue 

##Graphing
```{r}
ggplot(data = testdat, aes(x = Treatment, y = AbsorbanceCorrected, fill = Treatment)) + geom_boxplot() + xlab("Treatment") + ylab("Absorbance (L × mol-1 × cm-1)") + ggtitle("Absorbance Values of Homogenized Root Sample") + ylim(min = -0.03, max = 0.4)
```


```{r}
ggplot(data = dat, aes(x = Treatment, y = Anthocyanin_in_root, fill = Treatment)) + geom_boxplot() + ylim(min = 0, max = 3e-05) + xlab("Treatment") + ylab("Anthocyanin content (mol/g)") + ggtitle("Anthocyanin Content in Radish Root Tissue")
```
This ggplot is y limited between 0 and 3e-05 for better data visualization, it should be noted there are two extreme values in the PC treatment, one is below zero which is not a physically coherent value (negative concentration isn't really a thing) and the other is a very high concentration. This data will NOT be removed from the data analysis, as it is likely a result of biological variation; it is only removed here to allow for better visualization among treatments.


#STATISTICAL TESTING

##loading the other dataframe and running calculations
```{r}
testdat = read.csv("IRP Lab Data.csv")
testdat

testdat = testdat %>% mutate(testdat,
  Concentration_in_plate = AbsorbanceCorrected / (30000 * 0.5),
  Mol_in_plate = Concentration_in_plate * 0.2,
  Anthocyanin_in_root = Mol_in_plate/Sample.Weight
)
testdat #this data contains the 80% acetone we put in the plate to test for significant differences between the acetone and the samples. I just created two seperate CSVs, one with and without this data. The acetone data kept making the boxplot ugly, and I was unable to seperate the data in a clean manner with RStudio, hence the two dataframes.
```
Running a one way anova for the comparison of means amongst several groups

##ANOVA of corrected absorbance values
```{r}
corabsaov = aov(testdat$AbsorbanceCorrected ~ testdat$Treatment, data = testdat)
summary(corabsaov)

TukeyHSD(corabsaov)
```

##ANOVA of the concentrations
```{r}
concaov = aov(Anthocyanin_in_root ~ Treatment, data = dat)
summary(concaov)

TukeyHSD(concaov)
```

